---
title: "Week 2"
author: "Nick"
date: "2023-02-01"
---

```{r}

library(RMySQL)
library(tidyverse)
```
### Step 1: 
Define local database and log in as user DATA607.

```{r}

localdb_movies = dbConnect(MySQL(), user='DATA607', password=readLines("C:/data/SQLpass.txt"), dbname='week2_movies', host='localhost')

```



### STEP 2 :
Query localdb and save table into dataframe. Then disconnect as there is no need for additional data pull

```{r}
moviedf <- dbGetQuery(localdb_movies, "select * FROM week2_movies")
dbDisconnect(localdb_movies)
```

### STEP 3:
Looking through the data shows some entries were missing and non-numeric. Dataframe to be modified to include numeric data for analysis. 

```{r}

moviedf <- moviedf %>% mutate_if(is.character, as.numeric)
```
### STEP 4:
This is an attempt to see if there is correlation of how respondents rated the movies

``` {r}
movie.cor = cor(moviedf[2:6],use = "pairwise", method ="spearman")

library(corrplot)
plot<-corrplot(movie.cor, addCoef.col = 1,tl.cex = 0.5, method='number')
```

### STEP 5: 
Add one more row including average rating of each movie and plot on bar graph to summarize.

```{r}

moviedf<-rbind(moviedf, "Average" = colMeans(moviedf, na.rm=TRUE))
moviedf[[1]][11]<-"Average"

movie_names<-colnames(moviedf[2:7])
average_ranks<-as.numeric(moviedf[11,2:7])

plot_df<- data.frame(movie = c(movie_names),
                    average = c(average_ranks))

ggplot(plot_df, mapping=aes(x=average,y=movie)) + 
  geom_bar(stat = "identity") + ggtitle("Average Movie Ratings") + xlab("Average Rating")+ylab("Movie")
```

### SUMMARY: 
In this sample Empire Strikes Back was the highest rated movie overall, followed by Batman: The Dark Knight. A goal of the correlation plot was to see if the position of a movie in its trilogy (1st, 2nd or 3rd movie) could indicate how it was rated. Based on this sample there does not seem to be a strong correlation between how respondents rated each movie.
